\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \scshape\large\bfseries
}{}{0em}{}[\titlerule]

\setlist[itemize]{noitemsep, topsep=2pt}

\newcommand{\resumeItem}[1]{
  \item #1
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4}
  \end{tabular*}
}

\begin{document}

%================ HEADER =================
\begin{center}
  {\Huge \textbf{Nguyen Trong Chien}} \\[4pt]
  Ho Chi Minh City, Vietnam \\[2pt]
  +84 903 083 107 \quad | \quad
  \href{mailto:trongchien1711@gmail.com}{trongchien1711@gmail.com} \quad | \quad
  \href{https://linkedin.com/in/trongchien1711}{linkedin.com/in/trongchien1711} \quad | \quad
  \href{https://github.com/Trongchien1711}{github.com/Trongchien1711}
\end{center}

%================ SUMMARY =================
\section{Summary}
Data Analyst with a strong business background, specializing in transforming raw data into actionable insights. Proven track record in \textbf{automating manual reporting workflows}, reducing daily tasks by \textbf{85\%} and ensuring high data accuracy for executive decision-making. Skilled in building comprehensive data models (SQL, dbt) and interactive dashboards (Power BI) to support strategic planning in customer retention, inventory optimization, and cost control.

%================ EXPERIENCE =================
\section{Experience}

\resumeSubheading
{Business Data Analyst $|$ Assistant to BOD}{Oct 2025 -- Present}
{ERP Data \& Business Analytics}{Ho Chi Minh City}

\begin{itemize}
  \resumeItem{Developed and automated a reporting system from ERP source (MySQL), implementing an ELT pipeline that \textbf{reduced daily reporting time by 85\%} (from 4 hours to 15 minutes).}
  \resumeItem{Implemented data validation scripts using Python to track row counts and data freshness, ensuring high-quality metrics for executive reporting.}
  \resumeItem{Designed a comprehensive Data Model with 9 fact tables covering Sales, Inventory, and Costs to provide a single source of truth for the company.}
  \resumeItem{Built an \textbf{NPL (Raw Material) Cost Allocation Model} to distribute material costs across \textbf{72,000+ transaction lines}, enabling precise margin tracking per category.}
  \resumeItem{Performed \textbf{ABC/Pareto Analysis} on customer profiles, identifying key accounts contributing 80\% of revenue and proposing churn prevention strategies.}
  \resumeItem{Conducted \textbf{Inventory Health Audits}, identifying $\sim$20B VND in Work-in-Progress (WIP) overhead and low turnover rates (\textbf{0.6--0.83}), leading to Lean-based optimization proposals.}
  \resumeItem{Created \textbf{Executive Power BI Dashboards} (Glassmorphism UI) to visualize YoY growth and production efficiency KPIs.}
  \resumeItem{Identified a \textbf{"Revenue Paradox"} where Order volume increased 8.8\% but Revenue declined \textbf{0.5\%} due to a \textbf{8.55\% drop in AOV} and a \textbf{12.5\% decrease in UPT} (Units per Transaction).}
  \resumeItem{Automated the transition from manual Excel reporting to a near real-time automated system, improving data-driven decision turnaround from days to minutes.}
\end{itemize}

\resumeSubheading
{Sales Representative}{Sep 2022 -- Jun 2025}
{Hoa Sen Vietnam Food Processing JSC}{Ho Chi Minh City}

\begin{itemize}
  \resumeItem{Managed territory sales performance, consistently meeting revenue targets through data-informed area planning.}
  \resumeItem{Optimized weekly sales reporting by leveraging Excel and basic SQL to identify emerging trends and high-potential customer cohorts.}
\end{itemize}

%================ PROJECTS =================
\section{Projects}

\resumeSubheading
{ERP Data Reporting Pipeline (Portfolio Project)}{2026}
{SQL $\cdot$ dbt $\cdot$ PostgreSQL $\cdot$ Python}{\href{https://github.com/Trongchien1711/erp-dwh-td}{github.com/Trongchien1711/erp-dwh-td}}

\begin{itemize}
  \resumeItem{Developed an automated ELT pipeline: utilized \textbf{Watermark logic} for efficient incremental updates from MySQL ERP to PostgreSQL.}
  \resumeItem{Designed a \textbf{Star Schema} model with 9 fact tables and 9 dimensions, covering Sales, Raw Material Costs, and Inventory Health.}
  \resumeItem{Applied \textbf{dbt} for modular data transformation, organizing logic into Staging and Mart layers for maintainability.}
  \resumeItem{Implemented \textbf{Data Quality Tests} using dbt and Python to ensure referential integrity and data freshness.}
\end{itemize}

%================ EDUCATION =================
\section{Education}

\resumeSubheading
{University of Finance and Marketing}{2021}
{Bachelor of Business Administration}{Ho Chi Minh City}

%================ SKILLS =================
\section{Technical Skills}

\begin{itemize}
  \item \textbf{Data Analytics:} SQL (CTE, Window Functions, Joins), Business Intelligence, ABC/Pareto Analysis
  \item \textbf{Data Modeling:} Star Schema
  \item \textbf{Tools \& Visualization:} Power BI (DAX, Modeling), Advanced Excel (Power Query, Pivot)
  \item \textbf{Data Transformation:} dbt (Applied usage), Python (Pandas for ELT/EDA)
  \item \textbf{Workflow:} Git/GitHub
\end{itemize}

%================ CERTIFICATIONS =================
\section{Certifications}

\begin{itemize}
  \item IBM Data Analyst Professional Certificate -- Coursera (2025)
  \item HackerRank SQL (Advanced) Certificate (2025)
\end{itemize}

\end{document}
